An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-28 4_method.tex
lil update to appendix reference

To avoid evaluating the bisection angle at any location on all edges, we devise an efficient measure which operates only on the two nodes of an edge.
Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
\begin{align}\label{simple_significance_measure}
| R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)
\end{align}
(see \cref{distance_based_angles}).
This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \cref{edge_discretization}).
The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.

>>>>

To avoid evaluating the bisection angle at any location on all edges, we devise an efficient measure which operates only on the two nodes of an edge.
Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
\begin{align}\label{simple_significance_measure}
| R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)
\end{align}
(see \cref{distance_based_angles}).
This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \ref{edge_discretization}).
The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.
